Multi-reference pangenome graphs

### 2022-01-08 manuscript/fig_induction.tex
correct a bug
yes

%\node[roundnode]        (uppercircle)       [above=of seqA1] {1};
%\node[squarednode]      (rightsquare)       [below=of seqA1] {3};
%\node[roundnode]        (lowercircle)       [below=of seqA1] {4};

@@

\node[squarednode] (seqC1) [below of=seqB1] {G};
\node[squarednode] (seqC2) [right of=seqC1] {A};
\node[squarednode] (seqC3) [right of=seqC2] {T};
\node[squarednode] (seqC4) [right of=seqC3] {C};
\node[squarednode] (seqC5) [right of=seqC4] {A};

@@

\begin{scope}[node distance=1.3cm]
\node[roundnode] (g2) [below right = 3cm and 1.5cm of seqA1] {A};
\node[roundnode] (g1) [below left of=g2] {G};
\node[roundnode] (g3) [below right of=g1] {C};
\node[roundnode] (g4) [above right of=g3] {T};
\node[roundnode] (g5) [right of=g4] {T};
\node[roundnode] (g6) [right of=g5] {A};
\node[roundnode] (g7) [right of=g6] {C};
\node[roundnode] (g8) [above right of=g7] {A};
\node[roundnode] (g9) [below right of=g7] {G};
\end{scope}

@@

\begin{pgfonlayer}{bg}    % select the background layer
\draw[line width=0.5,color=red!100,looseness=1] (seqA1.south) to (g1);
\draw[line width=0.5,color=red!100,looseness=1] (seqB1.south) to (g1);
\draw[line width=0.5,color=red!100,looseness=1] (seqC1.south) to (g1);

\draw[line width=0.5,color={rgb:red,1;orange,1},looseness=1.0] (seqA2.south) to (g2);
\draw[line width=0.5,color={rgb:red,1;orange,1},looseness=1.0] (seqC2.south) to (g2);

\draw[line width=0.5,color=orange!100,looseness=1.0] (seqA3.south) to (g4);
\draw[line width=0.5,color=orange!100,looseness=1.0] (seqB3.south) to (g4);
\draw[line width=0.5,color=orange!100,looseness=1.0] (seqC3.south) to (g4);

\draw[line width=0.5,color=green!100,looseness=1.0] (seqA4.south) to (g5);
\draw[line width=0.5,color=green!100,looseness=1.0] (seqB4.south) to (g5);
%\draw[line width=0.5,color=blue!100,looseness=1.0] (seqC3.south) to (g4);

\draw[line width=0.5,color={rgb:blue,1;green,1},looseness=1.0] (seqA5.south) to (g6);
\draw[line width=0.5,color={rgb:blue,1;green,1},looseness=1.0] (seqB5.south) to (g6);

\draw[line width=0.5,color=blue!100,looseness=1.0] (seqA6.south) to (g7);
\draw[line width=0.5,color=blue!100,looseness=1.0] (seqB6.south) to (g7);

\draw[line width=0.5,color={rgb:blue,1;purple,1},looseness=1.0] (seqA7.south) to (g8);
\draw[line width=0.5,color={rgb:blue,1;purple,1},looseness=1.0] (seqC5.south) to (g8);

\draw[line width=0.5,color=purple!100,looseness=1.0] (seqB7.south) to (g9);

\draw[line width=0.5,color=gray,looseness=1.0] (seqB2.south) to (g3);

>>>>

@@

\node[squarednode] (seqC1) [below of=seqB1] {G};
\node[squarednode] (seqC2) [right of=seqC1] {A};
\node[squarednode] (seqC3) [right of=seqC2] {T};
\node[squarednode] (seqC4) [below of=seqB6] {C};
\node[squarednode] (seqC5) [right of=seqC4] {A};

@@

% alignments
\draw[line width=1.5,color=gray!50] (seqA1) -- (seqB1);
\draw[line width=1.5,color=gray!50] (seqA1) to [in=135,out=225,looseness=0.5, edge node={node [sloped,above] {}}] (seqC1);
%\draw[line width=1.0,color=gray!100] (seqA2) -- (seqB2);
\draw[line width=1.5,color=gray!50] (seqA2) to [in=135,out=225,looseness=0.5, edge node={node [sloped,above] {}}] (seqC2);

\draw[line width=1.5,color=gray!50] (seqA3) -- (seqB3);
\draw[line width=1.5,color=gray!50] (seqA3) to [in=135,out=225,looseness=0.5, edge node={node [sloped,above] {}}] (seqC3);
\draw[line width=1.5,color=gray!50] (seqB3) -- (seqC3);

\draw[line width=1.5,color=gray!50] (seqA4) -- (seqB4);
\draw[line width=1.5,color=gray!50] (seqA5) -- (seqB5);

%\draw[line width=1.5,color=gray!50] (seqA6) -- (seqB6);
\draw[line width=1.5,color=gray!50] (seqA6) to [in=135,out=225,looseness=0.5, edge node={node [sloped,above] {}}] (seqC4);
\draw[line width=1.5,color=gray!50] (seqB6) -- (seqC4);

%\draw[line width=1.5,color=gray!50] (seqA7) -- (seqB7);
\draw[line width=1.5,color=gray!50] (seqA7) to [in=135,out=225,looseness=0.5, edge node={node [sloped,above] {}}] (seqC5);
%\draw[line width=1.5,color=gray!50] (seqB7) -- (seqC5);

%    \draw (i) to[out=150, in=210, looseness=4, edge node={node [sloped,below] {$\leftarrow$}}] (l);
%    \draw (k) to[out=30, in=-30, looseness=4, edge node={node [sloped,above] {$\leftarrow$}}] (j);

%\begin{scope}[node distance=1cm]
\node[squarednode] (g2) [below = 0.75cm of seqC2] {A};
\node[squarednode] (g1) [below = 1.25cm of seqC1] {G};
\node[squarednode] (g3) [below = 0.5cm of g2] {C};
\node[squarednode] (g4) [below = 1.25cm of seqC3] {T};
\node[squarednode] (g5) [right of=g4] {T};
\node[squarednode] (g6) [right of=g5] {A};
\node[squarednode] (g7) [below = 1.25cm of seqC4] {C};
\node[squarednode] (g8) [below = 0.75cm of seqC5] {A};
\node[squarednode] (g9) [below = 0.5cm of g8] {G};
%\end{scope}

@@

\begin{pgfonlayer}{bg}    % select the background layer
\draw[line width=1.0,color=red!100] (seqA1) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g1);
\draw[line width=1.0,color=red!100] (seqB1) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g1);
\draw[line width=1.0,color=red!100] (seqC1) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g1);
%\draw[line width=1.0,color=red!100,looseness=0.5] (seqB1.south) to (g1.north);
%\draw[line width=1.0,color=red!100,looseness=0.5] (seqC1.south) to (g1.north);

\draw[line width=1.0,color={rgb:red,1;orange,1}] (seqA2) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g2);
\draw[line width=1.0,color={rgb:red,1;orange,1}] (seqC2) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g2);

\draw[line width=1.0,color=orange!100] (seqA3) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g4);
\draw[line width=1.0,color=orange!100] (seqB3) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g4);
\draw[line width=1.0,color=orange!100] (seqC3) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g4);

\draw[line width=1.0,color=green!100] (seqA4) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g5);
\draw[line width=1.0,color=green!100] (seqB4) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g5);
%\draw[line width=1.0,color=blue!100] (seqC3) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g4);

\draw[line width=1.0,color={rgb:blue,1;green,1}] (seqA5) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g6);
\draw[line width=1.0,color={rgb:blue,1;green,1}] (seqB5) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g6);

\draw[line width=1.0,color=blue!100] (seqA6) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g7);
\draw[line width=1.0,color=blue!100] (seqB6) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g7);
\draw[line width=1.0,color=blue!100] (seqC4) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g7);

\draw[line width=1.0,color={rgb:blue,1;purple,1}] (seqA7) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g8);
\draw[line width=1.0,color={rgb:blue,1;purple,1}] (seqC5) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g8);

\draw[line width=1.0,color=purple!100] (seqB7) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g9);

\draw[line width=1.0,color=brown] (seqB2) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g3);
